|

### 2023-01-23 paper_comparison/paper_comparison/paper_comparison.Rmd
Fix the plot size

```{r example-poly-lineup, fig.height=7, fig.cap="Lineup poly-24 in experiment I. Can you spot the most different plot? \\label{fig:example-poly-lineup}"}
VI_MODEL$plot_lineup(vi_lineup$poly_24$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

@@

```{r different-shape-of-heter, fig.height=2.67, fig.cap="Heteroskedasticity forms used in experiment II. Three different shapes (a = -1, 0, 1) are used in the experiment to create left-triangle, butterfly and right-triangle shapes."}

@@

```{r p-value-comparison, fig.width=8, fig.height=4, fig.cap="Rejection rate ($p$-value $<0.05$) of visual test conditional on the conventional test decision on non-linearity (left) and heteroskedasticity (right) lineups (uniform fitted values only) displayed using a mosaic plot. The visual test rejects less frequently than the conventional test. We would generally expect that the visual test would only reject when the conventional test does. Surprisingly, there is one lineup in the heteroskedasticity study where this is not the case. "}

@@

```{r different-x-dist-poly-power, fig.height = 3, fig.width = 7, fig.cap = "Power of conventional tests and visual tests on lineups produced by the non-linearity model under different fitted value distributions."}

@@

dat_different_dist %>%
  ggplot() +
  geom_smooth(data = ~filter(.x, x_dist == "Uniform"),
              aes(log_effect_size, 
                  reject), 
                  col = "grey", 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, size = 3) +
  geom_smooth(aes(log_effect_size, 
                  reject, 
                  col = x_dist), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              size = 1) +
  theme_light(base_size = 5) +
  scale_color_manual(values = rcartocolor::carto_pal(4, "Safe")[c(4,1,3,2)]) +
  scale_size_manual(values = c(1, 2, 3, 4)) +
  xlab(expression(log[e] (Effect_size))) +
  ylab("Power") +
  labs(col = "", linetype = "Test") +
  facet_wrap(~conv_or_not) +
  theme(legend.position="bottom")
```

```{r different-x-dist-heter-power, fig.height = 3, fig.width = 7, fig.cap = "Power of conventional tests and visual tests on lineups produced by the heteroskedasticity model under different distributions of regressor."}

@@

dat_different_dist %>%
  ggplot() +
  geom_smooth(data = ~filter(.x, x_dist == "Uniform"),
              aes(log_effect_size, 
                  reject), 
                  col = "grey", 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, size = 3) +
  geom_smooth(aes(log_effect_size, 
                  reject, 
                  col = x_dist), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              size = 1) +
  theme_light(base_size = 5) +
  scale_color_manual(values = rcartocolor::carto_pal(4, "Safe")[c(4,1,3,2)]) +
  scale_size_manual(values = c(1, 2, 3, 4)) +
  xlab(expression(log[e] (Effect_size))) +
  ylab("Power") +
  labs(col = "", linetype = "Test") +
  facet_wrap(~conv_or_not) +
  theme(legend.position="bottom")
```

@@

@@

```{r eval = FALSE}
poly_conv_sim %>%
  filter(x_dist == "uniform", shape %in% c(3, 4)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  select(shape, log_effect_size, (RESET3_p_value:RESET9_p_value)) %>%
  pivot_longer(RESET3_p_value:RESET9_p_value) %>%
  mutate(name = gsub("_p_value", " ", name)) %>%
  mutate(name = gsub("RESET", "", name)) %>%
  mutate(name = gsub("test", "", name)) %>%
  mutate(reject = as.numeric(value < 0.05)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject, col = name), 
              se = FALSE, 
              method = "glm",
              method.args = list(family = binomial())) +
  xlab(expression(log[e] (Effect_size))) +
  ylab("Power") +
  scale_color_manual(values = rev(rcartocolor::carto_pal(7, "RedOr"))) +
  theme_light() +
  labs(col = "RESET test order") +
  facet_wrap(~shape)
```

```{r poly-power-j, fig.cap = "Power of conventional tests and visual tests on lineups produced by the non-linearity model with four different shapes controlled by the parameter $j$."}

poly_conv_sim %>%
  filter(x_dist == "uniform") %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(reject = as.numeric(RESET4_p_value < 0.05)) %>%
  mutate(shape = c("U", "S", "M", "Triple-U")[shape]) %>%
  mutate(conv_type = "Conventional") %>%
  bind_rows(vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform", type == "polynomial") %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(reject = as.numeric(p_value < 0.05)) %>%
  mutate(shape = c("U", "S", "M", "Triple-U")[shape]) %>%
  mutate(conv_type = "Visual")) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject, col = factor(shape)), 
              se = FALSE, 
              method = "glm",
              method.args = list(family = binomial())) +
  xlab(expression(log[e] (Effect_size))) +
  ylab("Power") +
  scale_color_manual(values = rcartocolor::carto_pal(4, "Vivid")) +
  theme_light() +
  facet_wrap(~conv_type) +
  labs(col = "Non-linearity shape")
```

```{r heter-power-a, fig.cap = "Power of conventional tests and visual tests on lineups produced by the heteroskedasticity model with three different shapes controlled by the parameter $a$."}

heter_conv_sim %>%
  filter(x_dist == "uniform") %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(reject = as.numeric(BP_p_value < 0.05)) %>%
  mutate(a = c("left-triangle", "butterfly", "right-triangle")[a + 2]) %>%
  mutate(conv_type = "Conventional") %>%
  bind_rows(vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform", type == "heteroskedasticity") %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(reject = as.numeric(p_value < 0.05)) %>%
  mutate(a = c("left-triangle", "butterfly", "right-triangle")[a + 2]) %>%
  mutate(conv_type = "Visual")) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject, col = factor(a)), 
              se = FALSE, 
              method = "glm",
              method.args = list(family = binomial())) +
  xlab(expression(log[e] (Effect_size))) +
  ylab("Power") +
  scale_color_manual(values = rcartocolor::carto_pal(3, "Vivid")) +
  theme_light() +
  facet_wrap(~conv_type) +
  labs(col = "Heteroskedasticity shape")
```

@@

```{r p-value-comparison-old, eval = FALSE, fig.height=4, fig.cap="Visual test p-value compared to conventional test p-value for lineups produced by heteroskedasticity and non-linearity model. The scatter plot is drawn on a square root scale. Every dot on the plot corresponds to a lineup. Most of the dots are fallen on the left of the y = x line indicating visual test p-value is almost always higher than conventional test p-value. The blue curve is a smoothing of the dots showing a positive trend. "}
vi_survey %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(type = ifelse(type == "polynomial", "non-linearity", type)) %>%
  left_join(vi_survey %>% 
           count(unique_lineup_id) %>%
           rename(num_subject = n)) %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  mutate(type = factor(type, levels = c("non-linearity", "heteroskedasticity"))) %>%
  ggplot() +
  geom_abline() +
  geom_point(aes(conventional_p_value, p_value), alpha = 0.4) +
  geom_smooth(aes(conventional_p_value, p_value), se = FALSE, span = 0.6) +
  scale_x_sqrt() +
  scale_y_sqrt() +
  facet_wrap(~type) +
  ylab("Visual test p-value on square root scale") +
  xlab("Conventional test p-value on square root scale") +
  theme_light()
```

>>>>

```{r example-poly-lineup, fig.height = 7, fig.cap="Lineup poly-24 in experiment I. Can you spot the most different plot? \\label{fig:example-poly-lineup}"}
VI_MODEL$plot_lineup(vi_lineup$poly_24$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

@@

```{r different-shape-of-heter, fig.height = 2.67, fig.cap="Heteroskedasticity forms used in experiment II. Three different shapes (a = -1, 0, 1) are used in the experiment to create left-triangle, butterfly and right-triangle shapes."}

@@

```{r p-value-comparison, fig.width = 8, fig.height = 4, fig.cap="Rejection rate ($p$-value $<0.05$) of visual test conditional on the conventional test decision on non-linearity (left) and heteroskedasticity (right) lineups (uniform fitted values only) displayed using a mosaic plot. The visual test rejects less frequently than the conventional test. We would generally expect that the visual test would only reject when the conventional test does. Surprisingly, there is one lineup in the heteroskedasticity study where this is not the case. "}

@@

```{r different-x-dist-poly-power, fig.height = 4, fig.cap = "Power of conventional tests and visual tests on lineups produced by the non-linearity model under different fitted value distributions."}

@@

dat_different_dist %>%
  ggplot() +
  geom_smooth(data = ~filter(.x, x_dist == "Uniform"),
              aes(log_effect_size, 
                  reject), 
                  col = "grey", 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, size = 3) +
  geom_smooth(aes(log_effect_size, 
                  reject, 
                  col = x_dist), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              size = 1) +
  theme_light() +
  scale_color_manual(values = rcartocolor::carto_pal(4, "Safe")[c(4,1,3,2)]) +
  scale_size_manual(values = c(1, 2, 3, 4)) +
  xlab(expression(log[e] (Effect_size))) +
  ylab("Power") +
  labs(col = "", linetype = "Test") +
  facet_wrap(~conv_or_not) +
  theme(legend.position="bottom")
```

```{r different-x-dist-heter-power, fig.height = 4, fig.cap = "Power of conventional tests and visual tests on lineups produced by the heteroskedasticity model under different distributions of regressor."}

@@

dat_different_dist %>%
  ggplot() +
  geom_smooth(data = ~filter(.x, x_dist == "Uniform"),
              aes(log_effect_size, 
                  reject), 
                  col = "grey", 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, size = 3) +
  geom_smooth(aes(log_effect_size, 
                  reject, 
                  col = x_dist), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              size = 1) +
  theme_light() +
  scale_color_manual(values = rcartocolor::carto_pal(4, "Safe")[c(4,1,3,2)]) +
  scale_size_manual(values = c(1, 2, 3, 4)) +
  xlab(expression(log[e] (Effect_size))) +
  ylab("Power") +
  labs(col = "", linetype = "Test") +
  facet_wrap(~conv_or_not) +
  theme(legend.position="bottom")
```

@@

```{r poly-power-j, fig.height = 4, fig.cap = "Power of conventional tests and visual tests on lineups produced by the non-linearity model with four different shapes controlled by the parameter $j$."}

poly_conv_sim %>%
  filter(x_dist == "uniform") %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(reject = as.numeric(RESET4_p_value < 0.05)) %>%
  mutate(shape = c("U", "S", "M", "Triple-U")[shape]) %>%
  mutate(conv_or_not = "Conventional") %>%
  bind_rows(vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform", type == "polynomial") %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(reject = as.numeric(p_value < 0.05)) %>%
  mutate(shape = c("U", "S", "M", "Triple-U")[shape]) %>%
  mutate(conv_or_not = "Visual")) %>%
  mutate(shape = factor(shape, levels = c("S", "U", "M", "Triple-U"))) %>%
  select(shape, log_effect_size, reject, conv_or_not) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject, col = shape), 
              se = FALSE, 
              method = "glm",
              method.args = list(family = binomial())) +
  xlab(expression(log[e] (Effect_size))) +
  ylab("Power") +
  scale_color_manual(values = rcartocolor::carto_pal(4, "Vivid")) +
  theme_light() +
  theme(legend.position = "bottom") +
  facet_wrap(~conv_or_not) +
  labs(col = "Non-linearity shape")
```

@@

```{r heter-power-a, fig.height = 4, fig.cap = "Power of conventional tests and visual tests on lineups produced by the heteroskedasticity model with three different shapes controlled by the parameter $a$."}

heter_conv_sim %>%
  filter(x_dist == "uniform") %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(reject = as.numeric(BP_p_value < 0.05)) %>%
  mutate(a = c("Left-triangle", "Butterfly", "Right-triangle")[a + 2]) %>%
  mutate(conv_or_not = "Conventional") %>%
  bind_rows(vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform", type == "heteroskedasticity") %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(reject = as.numeric(p_value < 0.05)) %>%
  mutate(a = c("Left-triangle", "Butterfly", "Right-triangle")[a + 2]) %>%
  mutate(conv_or_not = "Visual")) %>%
  mutate(a = factor(a, levels = c("Left-triangle", "Butterfly", "Right-triangle"))) %>%
  select(a, log_effect_size, reject, conv_or_not) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject, col = a), 
              se = FALSE, 
              method = "glm",
              method.args = list(family = binomial())) +
  xlab(expression(log[e] (Effect_size))) +
  ylab("Power") +
  scale_color_manual(values = rcartocolor::carto_pal(3, "Vivid")) +
  theme(legend.position = "bottom") +
  theme_light() +
  facet_wrap(~conv_or_not) +
  labs(col = "Heteroskedasticity shape")
```

@@

```{r p-value-comparison-old, eval = FALSE, fig.height = 4, fig.cap="Visual test p-value compared to conventional test p-value for lineups produced by heteroskedasticity and non-linearity model. The scatter plot is drawn on a square root scale. Every dot on the plot corresponds to a lineup. Most of the dots are fallen on the left of the y = x line indicating visual test p-value is almost always higher than conventional test p-value. The blue curve is a smoothing of the dots showing a positive trend. "}
vi_survey %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(type = ifelse(type == "polynomial", "non-linearity", type)) %>%
  left_join(vi_survey %>% 
           count(unique_lineup_id) %>%
           rename(num_subject = n)) %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  mutate(type = factor(type, levels = c("non-linearity", "heteroskedasticity"))) %>%
  ggplot() +
  geom_abline() +
  geom_point(aes(conventional_p_value, p_value), alpha = 0.4) +
  geom_smooth(aes(conventional_p_value, p_value), se = FALSE, span = 0.6) +
  scale_x_sqrt() +
  scale_y_sqrt() +
  facet_wrap(~type) +
  ylab("Visual test p-value on square root scale") +
  xlab("Conventional test p-value on square root scale") +
  theme_light()
```
